The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_dtd.pdf}
    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
    \label{fig:onezone-dtd}
    \script{onezone_dtd.py}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_delay_taustar.pdf}
    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$). Tracks with $\tau_*=2$ Gyr are represented in black, while a track with a shorter $\tau_*=1$ Gyr is shown in red and a track with a longer $\tau_*=4$ Gyr is in yellow. The dotted, solid, and dashed black curves represent a minimum delay time of 40 Myr, 80 Myr, and 160 Myr, respectively. A power-law DTD is assumed in all models.}
    \label{fig:onezone-delay-taustar}
    \script{onezone_delay_taustar.py}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/onezone_plateau_width.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with a plateau DTD. The solid, dashed, and dot-dashed pink curves represent plateau widths $W=1.0$, 0.3, and 0.1 Gyr, respectively. All plateau DTDs assume a power-law slope of $\alpha=-1.1$. For comparison, the blue dotted curve represents an exponential DTD with a timescale $\tau=3$ Gyr, and the black dotted curve represents a power-law DTD with the same slope but no plateau.}
    \label{fig:onezone-plateau-width}
    \script{onezone_plateau_width.py}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_dtd.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
    \label{fig:onezone-dtd}
    \script{onezone_dtd.py}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_delay_taustar.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$). Tracks with $\tau_*=2$ Gyr are represented in black, while a track with a shorter $\tau_*=1$ Gyr is shown in red and a track with a longer $\tau_*=4$ Gyr is in yellow. The dotted, solid, and dashed black curves represent a minimum delay time of 40 Myr, 80 Myr, and 160 Myr, respectively. A power-law DTD is assumed in all models.}
    \label{fig:onezone-delay-taustar}
    \script{onezone_delay_taustar.py}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/onezone_sfh.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying star formation history (SFH). An exponential DTD with $\tau=1.5$ Gyr is assumed in all models.}
    \label{fig:onezone-sfh}
    \script{onezone_sfh.py}
\end{figure}
